% document properties
\documentclass[10pt,a4paper]{moderncv}

% theme
\moderncvtheme[blue]{casual}

% character encoding
\usepackage[utf8]{inputenc}
% disable hyphenation
\usepackage[none]{hyphenat}

% adjust the page margins
\usepackage[scale=0.85, left=1cm, right=1cm]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}						% if you want to change the width of the column with the dates
\footskip 60pt
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Yavor}
\familyname{Stoychev}
\mobile{(+359) 886 16 8983}
\email{stoychev.yavor@gmail.com}
\homepage{yavor.stoychev.bg}
\social[linkedin]{ystoychev}
\social[github]{voran}
\extrainfo{Last updated on \today. For updates, please visit my website. References available upon request.}
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

\nopagenumbers{}

\begin{document}
\maketitle

\section{Experience}
\cventry{Apr 2015 - }{Co-founder, Software Architect}{Perpetto.com}{Sofia, Bulgaria}{}{Building the eCommerce personalization software with #1 usability. Highly scalable and fault-tolerant, built on top of Hadoop, Spark, and Elasticsearch. We process millions of events to show each visitor on your eCommerce site products that are relevant to them. }
\cventry{Oct 2015 - Dec 2015}{Software Development Engineer II}{Amazon.com}{Seattle, WA, United States}{}{Working with the Global Fulfillment Optimization team to develop systems to dynamically schedule trucks to that fulfill Amazon orders in a fast and affordable fashion. }
\cventry{Oct 2013 - Oct 2015 }{Software Development Engineer}{Amazon.com}{Seattle, WA, United States}{}{Working with the Global Fulfillment Optimization team to develop enterpirse-grade, highly scalable systems
that optimize Amazon's supply chain and save its customers millions of dollars worth of shipping costs. }
\cventry{Jun 2013 - Sep 2013}{Software Developer}{Transmetrics}{Sofia, Bulgaria}{}{Developing an innovative IT product, which allows shipping companies to gain a critical few \% of capacity utilization, by finding and fixing the biggest problems first. I am leading the development of the user interface using Java Server Faces, HTML, and JavaScript.}
\cventry{Sep 2012 - Feb 2013}{Software Development Engineer Intern}{Amazon.com}{Seattle, WA, United States}{}{Developed a system for monitoring inventory shuffles in Java, HTML5, and JavaScript. The system receives input from downstream systems and records relevant data in a SQL database. This data is then analyzed and the resulting costs or savings are calculated and displayed on a web portal.}

\section{Education}
\cventry{Aug 2008 - Dec 2012}{Bachelor of Arts in Computer Science, Economics}{American University in Bulgaria}{Blagoevgrad, Bulgaria}{\textit{3.49/4}}{Minor in Mathematics. Dean's List for Fall 2008.}
\cventry{Aug 2011 - May 2012}{Bulgarian Young Leaders Program}{Rochester Institute of Technology}{Rochester, NY}{\textit{3.73/4}}{Dean's List for the duration of studies. Took courses in Economics,
Computer Science, and Mathematics.}
\cventry{Apr 2011 - Jul 2011}{Erasmus Student}{Otto-von-Guericke University}{Magdeburg, Germany}{}{Took courses in Computer Science and Economics.}
\cventry{Sep 2003 - May 2008}{High School Diploma}{First English Language School}{Sofia, Bulgaria}{\textit{5.75/6}}{Certificate of Excellence.}

\section{Favorite Tools}
\cvline{Languages}{\small Java, Scala, Ruby, Python, HTML5, JavaScript, C}
\cvline{Frameworks}{\small Rails, Spring, AngularJS, NodeJS}
\cvline{Big Data}{\small Octave, Spark, Hadoop, Elasticsearch, Matlab}
\cvline{IDEs}{\small Atom, Eclipse}
\cvline{Build / Deployment}{\small Make, Maven, SBT, Grunt, Ansible, Docker}
\cvline{Services}{\small Nginx, Tomcat, Unicorn, Hbase, Cassandra, Elasticsearch, Postgres}
\cvline{Operating Systems}{\small \{Debian, Ubuntu, Arch, Fedora, Red Hat Enterprise, CentOS\} Linux}

\section{Languages}
\cvlanguage{Bulgarian}{Native}{}
\cvlanguage{English}{Full Proficiency}{TOEFL: 115/120}
\cvlanguage{German}{Working Proficiency}{B1}

\section{Selected Activities}
\cvline{2013 - Present}{Member, Association of Software Engineers - Bulgaria}
\cvline{2012 - Present}{Member, Association of Bulgarian Leaders and Entrepreneurs}
\cvline{2011 - 2012}{Member, Free and Open Source Group at RIT}
\cvline{2008 - 2012}{Member, Computer Science Student Union at AUBG}

\section{Selected Achievements}
\cvline{2012}{Certificate, American Institute on Political and Economic Systems in Prague, Czech Republic}
\cvline{2011}{Fourth place at the  U.S. Northeastern Regional ACM Programming Competition}
\cvline{2011}{Selected to participate in the Cyber Defense Techniques Seminar at RIT}
\cvline{2010}{Bulgarian Young Leaders Award. Placed at the Rochester Institute of Technology}
\cvline{2010}{Selected for Erasmus Exchange at Otto-von-Guericke University for Spring 2011}
\cvline{2010}{America for Bulgaria Foundation Scholarship}
\cvline{2009}{Lou Hill Davidson and Ralph Davidson Scholarship}

\section{Senior Project: Computer Science}
\cvline{Title}{\emph{TAGS: A Graph-based Social Network}}
\cvline{Supervisors}{Prof. Volin Karagiozov}
\cvline{Description}{\small An extensible social network framework implemented in Java using the Neo4j graph database.}

\section{Selected Projects: Computer Science}
\cvline{Ruby on Rails, JS}{Books on Rails: A next-generation library management system}
\cvline{C++}{A student database with a command-line interface backed by a Binary Search Tree}
\cvline{C\#}{A simple sudoku solver}
\cvline{PHP, SQL, HTML}{Database Explorer: A web-based tool for database management}
\cvline{Python, GTK}{Sharescanner: A tool for indexing and downloading files from Samba shares}
\cvline{Assembly, C}{An application for encrypting and decrypting text using the XOR operator}
\cvline{UML, Teamwork}{Lead a team of four to design an interactive racing game written in Java}
\cvline{UML, Teamwork}{Worked in a team of four to design a touch-based 3D modeling application based on Blender}

\section{Courses}
\cvline{Computer Science}{Software Development Using C++, Fundamentals of Programming Languages, Database Systems, Assembly Language Programming, Computer Architecture, Object Oriented Languages, Fundamental Data Structures, Software Engineering, Algorithms, Advanced Database Models, Cyber Defense Techniques, User Interface Engineering, Information Security, Data Warehousing and Data Mining}
\cvline{Economics}{Principles of Macroeconomics, Principles of Microeconomics, Money and Banking, International Trade, International Finance, Quantitative Methods in Economics, Intermediate Macroeconomics, Intermediate Microeconomics, Econometrics, Economic Forecasting, Natural Resource Economics, Comparative Economic Systems}
\cvline{Mathematics}{Elementary Linear Algebra and Analytical Geometry, Calculus I - III, Differential Equations, Numerical Analysis}

\section{Papers: Economics}
\cvline{2012}{Stoychev, Yavor. Determinants of New Car Prices in the U.S. [Economic Forecasting]}
\cvline{2011}{Stoychev, Yavor. Hydrofracking: Rights, Risks, and Challenges [Natural Resource Economics]}



\section{Hobbies and Interests}
\cvline{Computer Science}{Algorithms, Operating Systems, Distributed Systems and Services}
\cvline{Economics}{Economic Policy, International Economics, Economic Forecasting}
\cvline{Mathematics}{Discrete Mathematics, Differential Equations}
\cvline{Sports}{Volleyball, Swimming, Skiing, Tennis}
\cvline{Outdoor}{Hiking, Camping, Travelling, Photography}
\cvline{Music}{Piano, Clarinet, Guitar Playing}

\end{document}
