% document properties
\documentclass[10pt,a4paper]{moderncv}
\footskip 45pt

% theme
\moderncvtheme[blue]{casual}

% character encoding
\usepackage[utf8]{inputenc}
% disable hyphenation
\usepackage[none]{hyphenat} 

% adjust the page margins
\usepackage[scale=0.9]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{2cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Yavor}
\familyname{Stoychev}  
\address{37 Shipchenski Prohod Blvd vh. B ap. 39}{Sofia 1111, Bulgaria}
\mobile{(+359) 886 16 8983}
\phone{(+359 2) 873 4717}
\email{stoychev.yavor@gmail.com} 
\homepage{yavor.stoychev.info}
\extrainfo{Last updated on \today. For updates, please visit my website. References available upon request.}
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted


\nopagenumbers{}


\begin{document}
\maketitle

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{Aug 2008 - Dec 2012}{Bachelor or Arts in Computer Science, Economics}{American University in Bulgaria}{Blagoevgrad, Bulgaria}{\textit{3.49/4}}{Minor in Mathematics. Dean's List for Fall 2008.}
\cventry{Aug 2011 - May 2012}{Bulgarian Young Leaders Program}{Rochester Institute of Technology}{Rochester, NY}{\textit{3.73/4}}{Dean's List for the duration of studies. Took courses in Economics, 
Computer Science, and Mathematics.}
\cventry{Apr 2011 - Jul 2011}{Erasmus Student}{Otto-von-Guericke University}{Magdeburg, Germany}{}{Took courses in Computer Science and Economics.}
\cventry{Sep 2003 - May 2008}{High School Diploma}{First English Language School}{Sofia, Bulgaria}{\textit{5.75/6}}{Certificate of Excellence.}

\section{Experience}
\cventry{Jun 2013 - }{Software Developer}{Transmetrics}{Sofia, Bulgaria}{}{Developing an innovative IT product, which allows shipping companies to gain a critical few \% of capacity utilization, by finding and fixing the biggest problems first. My main roles and responsibilities involve the data presentation and visualization components of the system.}
\cventry{Sep 2012 - Feb 2013}{Software Development Engineer Intern}{Amazon.com}{Seattle, WA, United States}{}{Developed a system for monitoring inventory shuffles in Java, HTML5, and JavaScript. The system receives input from downstream systems and records relevant data in a SQL database. This data is then analyzed and the resulting costs or savings are calculated and displayed on a web portal.}

\section{Courses}
\cvline{Computer Science}{Software Development Using C++ (Placement Test), Fundamentals of Programming Languages, Database Systems, Assembly Language Programming, Computer Architecture, Object Oriented Languages, Fundamental Data Structures, Software Engineering, Algorithms, Advanced Database Models, Cyber Defense Techniques, User Interface Engineering, Information Security, Data Warehousing and Data Mining, Senior Project I}
\cvline{Economics}{Principles of Macroeconomics, Principles of Microeconomics, Money and Banking, International Trade, International Finance, Quantitative Methods in Economics, Intermediate Macroeconomics, Intermediate Microeconomics, Econometrics, Economic Forecasting, Natural Resource Economics, Comparative Economic Systems}
\cvline{Mathematics}{Elementary Linear Algebra and Analytical Geometry, Calculus I - III, Introduction to Differential Equations, Numerical Analysis}

\section{Senior Project: Computer Science}
\cvline{Title}{\emph{TAGS: A Graph-based Social Network}}
\cvline{Supervisors}{Prof. Volin Karagiozov}
\cvline{Description}{\small An extensible social network framework implemented in Java using the Neo4j graph database.} 

\section{Projects: Computer Science}
\cvline{C++}{A student database with a command-line interface backed by a Binary Search Tree}
\cvline{C\#}{A simple sudoku solver}
\cvline{PHP, SQL, HTML, JS}{Database Explorer - A web-based tool for database management}
\cvline{Python, GTK}{Sharescanner - A tool for indexing and downloading files from Samba shares}
\cvline{Assembly, C}{An application for encrypting and decrypting text using the XOR operator}
\cvline{UML, Teamwork}{Lead a team of four to design an interactive racing game written in Java}
\cvline{UML, Teamwork}{Worked in a team of four to design a touch-based 3D modeling application based on Blender}

\newpage

\section{Papers: Economics}
\cvline{2012}{Stoychev, Yavor. Determinants of New Car Prices in the U.S. [Economic Forecasting]}
\cvline{2011}{Stoychev, Yavor. Hydrofracking: Rights, Risks, and Challenges [Natural Resource Economics]}


\section{Languages}
\cvlanguage{Bulgarian}{Native}{}
\cvlanguage{English}{Full Proficiency}{TOEFL: 115/120}
\cvlanguage{German}{Working Proficiency}{B1}

\section{Skills: Computer Science}
\cvline{Languages}{\small IA-32 Assembly, C, C++, Java, Perl, Python, Ruby, HTML5, JavaScript, SQL, PHP, UML}
\cvline{IDEs}{\small Eclipse, Netbeans, MS Visual Studio}
\cvline{Version Control}{\small Git, Subversion}
\cvline{Build Tools}{\small Ant, Maven, GCC}
\cvline{Services}{\small Apache Web Server, Apache Tomcat, Jetty, Nginx, OpenVPN, MySQL, Oracle, Samba}
\cvline{Libraries}{\small GTK, QT, Spring, Neo4j, JUnit, jQuery, Hibernate}
\cvline{Operating Systems}{\small \{Debian, Ubuntu, Arch, Fedora, Red Hat Enterprise, CentOS\} Linux, *BSD}

\section{Skills: Economics}
\cvline{Software}{\small Stata, Matlab}


\section{Selected Activities}
\cvline{2012 - Present}{Member, Association of Bulgarian Leaders and Entrepreneurs}
\cvline{2011 - 2012}{Member, RIT Linux Users Group}
\cvline{2011 - 2012}{Member, Free and Open Source Group at RIT}
\cvline{2009 - 2011}{Member, Freakonomics Club at AUBG}
\cvline{2008 - Present}{Senior Member, Computer Science Student Union at AUBG}
\cvline{2004 - Present}{Member, Astronomy Association Sofia}
\cvline{2003 - 2005}{Member, Physics Society  First English Language School Sofia}

\section{Selected Achievements}
\cvline{2012}{Certificate, American Institute on Political and Economic Systems in Prague, Czech Republic}
\cvline{2011}{Fourth place at the  U.S. Northeastern Regional ACM Programming Competition}
\cvline{2011}{Selected to participate in the Cyber Defense Techniques Seminar at RIT}
\cvline{2010}{Bulgarian Young Leaders Award. Placed at the Rochester Institute of Technology}
\cvline{2010}{Selected for Erasmus Exchange at Otto-von-Guericke University for Spring 2011}
\cvline{2010}{America for Bulgaria Foundation Scholarship}
\cvline{2009}{Lou Hill Davidson and Ralph Davidson Scholarship}
\cvline{2008}{Certificate of Merit for High Overall Grades in the First English Language School}
\cvline{2008}{Certificate for Participation, 50th Anniversary Concert of the First English Language School}
\cvline{2008}{Certificate of Merit for Contributions to the School Brass Band}
\cvline{2007}{Certificate of Merit for Excellent Performance in the Melpomene Drama Contest}
\cvline{2006}{Prize, "Physics through my Eyes" Student Conference in Yambol, Bulgaria}

\section{Hobbies and Interests}
\cvline{Computer Science}{Algorithms, Operating Systems, Distributed Systems and Services}
\cvline{Economics}{Economic Policy, International Economics, Economic Forecasting}
\cvline{Mathematics}{Discrete Mathematics, Differential Equations}
\cvline{Sports}{Volleyball, Swimming, Skiing, Tennis}
\cvline{Outdoor}{Hiking, Camping, Travelling, Photography}
\cvline{Music}{Piano, Clarinet, Guitar Playing}

\end{document}
